---
title: 'P8105: Homework 1'
author: "Derek Lamb"
date: "`r Sys.Date()`"
output: github_document
---

# Problem 1

```{r load packages, message = FALSE}
# I initially installed this package, but now have commented it out
# install.packages('moderndive')

library(moderndive)
```

Now I will load the dataset for this problem and pull some basic information about it.

```{r data import}

data("early_january_weather")
#summary.data.frame(early_january_weather)
#table(early_january_weather$origin)
```

This data set contains `r nrow(early_january_weather)` recorded values of `r ncol(early_january_weather)` variables. The variables listed include the:

-   Origin of each data point [Newark Liberty Airport for all data]
-   Date and time for each data point, including:
    -   Year [2013 for all]
    -   Month [January for all]
    -   Day [ranging from 1-15]
    -   Hour [ranging 0-23]
    -   Combined variable with all four values included
-   Temperature and dew point [in °F]
-   Relative humidity [%]
-   Wind direction [in degrees], speed, and gust speed [mph]
-   Precipitation [in inches]
-   Sea level pressure [mbar]
-   Visibility [miles]
