---
title: 'P8105: Homework 1'
author: "Derek Lamb"
date: "`r Sys.Date()`"
output: github_document
---

# Problem 1

```{r load packages, message = FALSE}
# I initially installed this package, but now have commented it out
# install.packages('moderndive')

# Loading the packages that are needed for the assignment
library(moderndive)
library(tidyverse)
```

## Data description

Now I will load the dataset for this problem and pull some basic information about it.

```{r data import}

data("early_january_weather")

```

This data set contains `r nrow(early_january_weather)` recorded values of `r ncol(early_january_weather)` variables. The variables listed include the:

-   Origin of each data point [Newark Liberty Airport for all data]
-   Date and time for each data point, including:
    -   Year [2013 for all]
    -   Month [January for all]
    -   Day [ranging from 1-15]
    -   Hour [ranging 0-23]
    -   Combined variable with all four values included
-   Temperature and dew point [in °F]
-   Relative humidity [%]
-   Wind direction [in degrees], speed, and gust speed [mph]
-   Precipitation [in inches]
-   Sea level pressure [mbar]
-   Visibility [miles]

The variables *wind direction*, *wind gust speed*, and *pressure* are missing data.

### Average temperature
During the 15 days of 2013, the average temperature at Newark Liberty Airport was `r round(mean(early_january_weather$temp), digits = 1)`°F.

## Ploting temperature over time

I will make a plot of temperature over time using `ggplot2` and save it using `ggsave()`.

```{r temp v time plot}
# Make the plot of temp v time, and color based upon humidity
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() +
  
# Fix axis labels and ticks
  labs(title = "Newark Airport Temperature January 2013", 
       x = "Date",
       y = "Temperature (°F)",
       color = "Humidity (%)") +
  scale_x_datetime(date_breaks = "3 days", date_labels = "%b %d") +
  scale_y_continuous(n.breaks = 8, limits = c(25,60)) +
  
# Change theme and reposition legend
  theme_classic() +
  theme(legend.position = "top")

# Save the plot as a png in the directory
ggsave(file = "EWR_temp_2013_01.png")
```

The temperature at Newark Liberty Airport oscillates from day to night, and appears to be rising over the first two weeks of January 2013, before falling on the final day (January 15). The humidity tends to be low and steady for the first week, although there is some rising humidity at points of low temperature (i.e. at night). For a few days during the second week, there is high humidity consistently, and this is associated with a stabilization of the temperature.

# Problem 2
I will make a dataframe containing one numeric, one logical, one character, and one factor vector.

```{r make dataframe}
df_2 <- tibble(
  vec_norm = rnorm(10),
  vec_bool = (vec_norm > 0),
  vec_char = letters[1:10],
  vec_factor = factor(c("A","A","A","B","B","B","C","C","C","C"))
)
```

I will now try to take the mean of each variable in the dataframe.

```{r take means df}
for (i in 1:4) {
  print(mean(pull(df_2,i)))
}

```

The first and second variables (standard normal and logical operator) provide means of `r mean(pull(df_2,1)` and `r mean(pull(df_2,2)` respectively. The character vector and the factor vector returned errors when I tried to take the mean.
